Verifying Demonstrations

### 2019-09-11 paper/DB-anon-cred.tex
Adds conclusion to DH resistance proof
Minor fixes for formulations

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields a success with probability 
    \(\frac{1}{k}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
  thus \(\left(\frac{1}{k}+\frac{1}{q}\right)^n\) in total per protocol 
  session.
\end{proof}

@@

\begin{theorem}[\acs*{DBDH} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = X\).
  % XXX compute DH resistance probability
\end{theorem}

@@

  This yields that \(R' = g^{\rho'}\) should equal \(g^{s_i} A'^{c_i} = g^{\rho 
      - c_i' \alpha} (g^{\alpha'})^{c_i} = g^{\rho - c_i' \alpha + c_i 
      \alpha'}\).
  Both \(\rho\) and \(\alpha\) are unknown to the adversary and the adversary 
  cannot choose \(c_i\).
  The adversary needs \(\rho' - \rho = c_i \alpha' - c_i' \alpha\).
  We thus have that \[\Adv_{\DBS}^{\text{DH}}(\adv) = \Prob{\rho' - c_i \alpha' 
      = \rho - c_i' \alpha} = X,\]
  which concludes the proof.
\end{proof}

The last property is \ac{DBTF}.

\begin{proof}[\acs*{DBTF} resistance]
  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
  provers help with non-negligible advantage~\(\epsilon\), \ie the success 
  probability is \(\frac{1}{2}+\epsilon\).
  There is chance that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
  Thus, there is some case for which \(\adv\) knows both responses.
  In that case \(\adv\) can simply compute the secret and impersonate with 
  probability \(1\) forever.
\end{proof}

The protocol is \ac{DBTF}-resistant.
Indeed, if the malicious prover gives both responses to the accomplice, the 
accomplice can compute his secret key.
The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).

>>>>

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields success with probability 
    \(\frac{1}{k}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
  thus \(\left(\frac{1}{k}+\frac{1}{q}\right)^n\) in total per protocol 
  session.
\end{proof}

@@

\begin{theorem}[\acs*{DBDH} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q}\).
\end{theorem}

@@

  This yields that \(R' = g^{\rho'}\) should equal \(g^{s_i} A'^{c_i} = g^{\rho 
      - c_i' \alpha} (g^{\alpha'})^{c_i} = g^{\rho - c_i' \alpha + c_i 
      \alpha'}\).
  Both \(\rho\) and \(\alpha\) are unknown to the adversary and the adversary 
  cannot choose \(c_i\).
  The adversary needs \(\rho' = \rho - c_i' \alpha + c_i \alpha'\).
  Let \(\rho'\) and \(c_i'\) be fixed (say 0), then we have that \(\alpha' = 
    \rho c_i^{-1}\).
  We thus have that
  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \Prob{\rho' - c_i \alpha' = \rho - c_i' 
      \alpha} = \frac{1}{q}\),
  which concludes the proof.
\end{proof}

The last property is \ac{DBTF}.
The protocol is \ac{DBTF} resistant.
Indeed, if the malicious prover gives both responses to the accomplice, the 
accomplice can compute his secret key.
And any help will increase the probability of success of future attempts.

\begin{theorem}[\acs*{DBTF} resistance]
  \dots
\end{theorem}

\begin{proof}
  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
  provers help with non-negligible advantage~\(\epsilon < \frac{1}{2}\), \ie 
  the success probability is \(\frac{1}{2}+\epsilon\).
  The probability that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
  Since \(\epsilon\) is non-negligible, there is some case for which \(\adv\) 
  knows both responses.
  In that case \(\adv\) can simply compute the secret and impersonate with 
  probability \(1\) forever, which contradicts our assumption about 
  \(\epsilon\).
\end{proof}
